\begin{thebibliography}{9}
% The bibligraphy is mandatory. Here you have a couple of examples (remember to put references in the text).

\bibitem{pattnoise}
Teledyne Photometrics, \emph{Pattern Noise: DSNU and PRNU}, \url{photometrics.com}

\bibitem{oxidecmosPUF}
Chuang, K.H.; Bury, E.; Degraeve, R.; Kaczer, B.; Groeseneken, G.; Verbauwhede, I.; Linten, D. Physically unclonable function
using CMOS breakdown position. In Proceedings of the IEEE International Reliability Physics Symposium (IRPS), Monterey, CA,
USA, 2-6 April 2017; p. 4C-1.

\bibitem{pixelvarPUF}
Okura, S.; Nakura, Y.; Shirahata, M.; Shiozaki, M.; Kubota, T.; Ishikawa, K.; Takayanagi, I.; Fujino, T. P01 A Proposal of PUF
Utilizing Pixel Variations in the CMOS Image Sensor

\bibitem{SRAMPUF}
Arjona, R.; Prada-Delgado, M.A.; Arcenegui, J.; Baturone, I. Using Physical Unclonable Functions for Internet-of-Thing Security
Cameras. In Interoperability, Safety and Security in IoT; Springer: Berlin/Heidelberg, Germany, 2017; pp. 144-153.

\bibitem{campuf}
Kim Younghyun, Lee Yongwoo (2018) \emph{CamPUF: Physically Unclonable Function based on CMOS Image Sensor Fixed Pattern Noise}, IEEE Design Automation Conference 2018.

\bibitem{dataset}
Kim Younghyun, Lee Yongwoo (2018) \emph{CamPUF Dataset}, \url{https://wisest.ece.wisc.edu/research-old/mobile-and-embedded-security/campuf-dataset/}.

\bibitem{temperature}
Kenji Irie, Alan E. McKinnon, Keith Unsworth, Ian Woodhead, (2009) \emph{Measured effects of temperature on illumination-independent camera noise}, IEEE.

\bibitem{jpeg}
Marina Gardella, Tina Nikoukhah, Yanhao Li, Quentin Bammey, (2022) \emph{The Impact of JPEG Compression on Prior Image Noise}.  IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP 2022), May 2022, Singapore. pp.2689-2693.

\end{thebibliography}